Spurious Sentience:\\ Dovelating Inflated AI World Model Claims \raisebox{-6pt}{\includegraphics[scale=0.09]{dove_1f54a-fe0f.png}}

### 2024-01-25 main.tex

Present work case studies an example of claims of observed AGI 'sparks' in AI research, and reviews work on two human phenomena that are likely to lead to false claims: anthropomorphism, or the attribution of human-like qualities to non-human objects, and confirmation bias, or the seeking-out and/or biased interpretation of evidence in support of one's beliefs. We describe how these phenomena may interact in the context of AI research and development, leading to especially poor inferences about the degree of general intelligence, or lack thereof, of AI systems. We further show results from experiments that at first appear to indicate nascent 'sparks' of AGI, but that stronger tests show are indications of spurious sparks.

@@

\includegraphics[width=0.5\textwidth]{results/figures/measures_CPI (n_pc=128).png}

@@

@@

\includegraphics[width=0.5\textwidth]{results/figures/attack_inflation.png}

>>>>

Present work case studies an example, to which claims of observed AGI 'sparks' in AI research, and reviews work on two human phenomena that are likely to lead to false claims: anthropomorphism, or the attribution of human-like qualities to non-human objects, and confirmation bias, or the seeking-out and/or biased interpretation of evidence in support of one's beliefs. We describe how these phenomena may interact in the context of AI research and development, leading to especially poor inferences about the degree of general intelligence, or lack thereof, within AI systems. We further display results from experiments that at first appear to indicate nascent 'sparks' of AGI, but that stronger tests show are indications of spurious sparks.

@@

\includegraphics[width=1.0\textwidth]{results/figures/rmse_pca_128.png}

@@

\includegraphics[width=1.0\textwidth]{results/figures/attack_all_measures.png}

@@
